Command, analyse and data mining of a chromatograph during drilling operations

### 2018-11-28 papers/chromatography (for ethics course)/paper.tex
Abstract and introduction written on chroma paper

\title{Comanda, analiza și prelucrarea datelor a unui cromatograf de proces
}

@@

\begin{abstract}
Realizarea unei aplicații de achiziții a datelor provenite dintr-un cromatograf de proces. 
Prelucrarea datelor se face printr-o funcție de liniarizare specifică fiecărui aparat, printr-o funcție de calibrare iar apoi,
rezultatele sunt trecute într-o bază de date special proiectată pentru aplicații de urmărire geologică. 
Totodată, în funcție de performanțele constructive ale aparatului, se face comanda lui prin porturi digitale.
\end{abstract}

\begin{IEEEkeywords}
cromatografie, , style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

@@

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

>>>>

\title{Command, analyse and data mining of a chromatograph during drilling operations
}

@@

\begin{abstract}
    Chromatograph analyses need a great attention to the way results are generated and how they are calibrated.
    At the same time the construction and maintenance need to be simple and quick such that any operation which
    needs to be made on a chromatograph doesn't stop the entire drilling crew.
\end{abstract}

\begin{IEEEkeywords}
chromatography, geology, mud-logging
\end{IEEEkeywords}

\section{Introduction}
    During drilling operations, while seeking gas or oil, certain gas analyses must be taken.
    Those analyses are performed by a special device called chromatograph. 
    Present paper presents a novel way of generating the mathematical model of a chromatograph during its construction
    and then using this model to ensure the results accuracy.
\section{chromatograph}

\subsection{Construction}

@@

\subsection{Maintenance}

\section{Mathematical model}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.
